Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-03-16 Submission.Rmd
revised intro

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes. We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource. We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

@@

Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework. First, research on the job demands-resources model @demerouti2001job and later job demands-resources theory @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. The job demands-resources theory distinguishes between resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

@@

>Hyp 3.a: Job resources are positively associated with engagement.

>Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.

>Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.

ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) *are there characteristics that are more likely to vary across demand and resource*, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes. We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource. We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

@@

Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework. The job demands-resources model @demerouti2001job,  @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. The job demands-resources theory distinguishes between resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

@@

>Hyp 3.a: Engagement is predicted by resources and challenges.

>Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.

ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS 2017 JOHP moving forward
